\paragraph{EWA Splatting}

EWA Splatting \cite{zwickerEWAVolumeSplatting2001} \cite{zwickerEWASplatting2002} 
is a high-quality splatting method based on Gaussian kernels.
The idea is based on Heckbert's EWA (Elliptical Weighted Average) filter for texture mapping.

\subparagraph{Splatting Equation}

\input{splatting_equation_deduction}

The coordinate $\hat{\mathbf{x}}=(x_0,x_1)$ is called 
the screen space coordinate, and we can say that 
$I_\lambda(\hat{\mathbf{x}})$ and $q_k(\hat{\mathbf{x}})$
are defined in \textit{screen space}

splatting is attractive because it only requires the 
precomputed 2D convolution kernels. In contrast, ray
casting methods require the 3D convolution kernels.

\subparagraph{EWA Volome Resampling Filter}

The splatting equation (\ref{eq:splatting_equation}) represents
the output image as a continuous 2D function, 
but in practice, it will be sampled at discrete pixel locations.
So it has to be band-limited to respect to Nyquist frequency of the grid, 
to avoid aliasing.

By appling an appropriate low-pass filter $h(\hat{\mathbf{x}})$,
we have 

$$(I_\lambda \otimes h)(\hat{\mathbf{x}})=
    \int_{\mathbb{R}^2}\sum\limits_{k }\limits^{} 
    c_{\lambda k}(\mu)g_kq_k(\mu)\prod\limits_{j=0}\limits^{k-1} 
    (1-g_jq_j(\mu))h(\hat{\mathbf{x}}-\mu)d\mu $$

we make two more assumptions

\begin{enumerate}
    \item the emission coefficient is approximately constant in supporting area $c_{\lambda x}$
    \item ignore the effect of shading 
    \item the attenuation factor is approximately constant 
\end{enumerate}

Thus we have 

$$\rho_k(\hat{\mathbf{x}})=(r_k \otimes h)(\hat{\mathbf{x}})$$

The resampling filter is strongly space-variant.

Swan et al. present uniform low-pass filter.

But our method provides non-uniform scaling in these cases.

\subparagraph{Elliptical Gaussian Kernel}

We choose Elliptical Gaussian Kernel 

TODO: Gaussian Transform